\documentclass[main.tex]{subfiles}

\begin{document}
	% ============================================================
	% acknowledgments
	% ============================================================
    \codedataavailability{The source codes for \pyinline{ifs-physics-common} \citep[][\url{https://github.com/stubbiali/ifs-physics-common}]{ifs-physics-common}, CLOUDSC-GT4Py \citep[][\url{https://github.com/stubbiali/gt4py-dwarf-p-cloudsc}]{gt4py-dwarf-p-cloudsc} and CLOUDSC2-GT4Py \citep[][\url{https://github.com/stubbiali/gt4py-dwarf-p-cloudsc2-tl-ad}]{gt4py-dwarf-p-cloudsc2-tl-ad}, as well as the data and scripts to produce all the figures of the paper \citep[][\url{https://github.com/stubbiali/cloudsc-paper}]{gmd-cloudsc-paper}, are available on Github and archived on Zenodo.}

	%% this section is mandatory
	\authorcontribution{SU ported the CLOUDSC and CLOUDSC2 dwarfs to Python using GT4Py and ran all the numerical experiments presented in the paper, under the supervision of CK and HW. SU further contributed to the development of the infrastructure code illustrated in Section \ref{section:infrastructure-code}, under the supervision of CS, LS and TCS. MS made relevant contributions to the Fortran and C reference implementations of the ECMWF microphysics schemes. SU and CK wrote the paper, with feedback from all co-authors.}

	%% this section is mandatory even if you declare that no competing interests are present
	\competinginterests{The authors declare that they have no conflict of interest.}

	%% optional section
	%\disclaimer{TEXT}

	\begin{acknowledgements}
	    \review{We would like to thank three anonymous referees for carefully reviewing the manuscript and providing many constructive comments.} This study was conducted as part of the Platform for Advanced Scientific Computing (PASC) funded project KILOS (``Kilometer-scale non-hydrostatic global weather forecasting with IFS-FVM''), which also provided us with computing resources on the Piz Daint supercomputer at CSCS. \review{CK acknowledges support from the ESiWACE3 project funded by the European High Performance Computing Joint Undertaking (EuroHPC JU) and the European Union (EU) under grant agreement No 101093054.} We \review{additionally} acknowledge EuroHPC JU for awarding the project ID 200177 access to the MeluXina supercomputer at LuxConnect and the project ID 465000527 access to the LUMI system at CSC, and thank Thomas Geenen and Nils Wedi from Destination Earth for their help. We are grateful to Michael Lange and Balthasar Reuter for discussions and support regarding IFS codes.
	\end{acknowledgements}

    %\biblio
\end{document}
